% Curriculum Vitae Template Latex Code by dobri student %

%%%%%%%%%%%%%%%%%%%%%%%%%%%% Document Specifications %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt]{article} 
\usepackage{anysize}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{setspace} % Allows for line spacing adjustments

\usepackage[a4paper, left=0.75in, right=0.75in, top=1in, bottom=1in]{geometry}
\setstretch{0.5}  % Slightly tighter line spacing


% For item symbol
\usepackage{fontawesome}
\usepackage{enumitem}
\setlist[itemize]{label=\faAngleRight}

\pagenumbering{arabic}
\begin{document}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Name & Contact Info %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begingroup
\setstretch{1.2}
\begin{center}
	{\Large \bfseries Ing. Michal Fusatý} \\ 
	{\large Curriculum Vitae} 	
\end{center}
\endgroup


\begin{center}
	\noindent
	\href{mailto:fusaty@proton.me}{fusaty@proton.me} \\ 
	+421 949 743 031 \\
\end{center}
	\noindent
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries Education}
\end{center} 

\noindent
{\bfseries Master's in Computer Science} \hfill 2018 - 2023\\ 
\noindent \href{https://www.fei.stuba.sk/english.html?page_id=793}{Slovak Technical University, FEI} \hfill Bratislava
\noindent

\vspace{0.1in}

\noindent
{\bfseries High school education} \hfill 2014 - 2018\\ 
\noindent \href{https://gymziar.edupage.org/}{Gymnázium Milana Rúfusa}  \hfill Žiar nad Hronom
\noindent


\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% JOB EXPERIENCE-FULL  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	{\noindent \bfseries Job Experience} \\
	{full-time}
\end{center}

\noindent
{\bfseries Junior Cybersecurity Engineer} \hfill February 2023 - Present \\  
\noindent \href{https://www.framatome.com/en/about/}{Framatome Controls s.r.o.} \hfill Bratislava
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Conducting vulnerability assessments and scanning to identify and address potential security risks in the critical infrastructure of nuclear power plants.
\item Hardening, and testing the hardening of I\&C systems and personal computers.
\item Helping with development of SIEM and log collection software for I\&C systems.
\item Developing software tools for penetration testing and collaborated with software development teams to help them implement secure coding practices.
\item Designing and deploying network infrastructure to ensure optimal performance and security.
\end{itemize}

\vspace{0.2in} %between 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% JOB EXPERIENCE-PART  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries Job Experience} \\
	{part-time}
\end{center}

\noindent
{\bfseries Junior Web Developer} \hfill March 2022 - December 2022 \\  
\noindent \href{https://www.softec.sk/en/about-us}{SOFTEC, spol. s r.o.} \hfill Bratislava 
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Contributed to the development and deployment of multiple full-stack banking web applications, utilizing Java, Javascript, and AngularJS.
\end{itemize}


\noindent
{\bfseries System Application Administrator Intern} \hfill October 2021 - March 2022 \\  
\noindent \href{https://www.tatrabanka.sk/en/about-bank/about-tatra-banka/}{Tatra banka a.s.} \hfill Bratislava 
\begin{itemize} \itemsep -2pt % Reduce space between items
%	\item Internship within the IT Academy of Tatra banka 
\item Utilized Nagios, Dynatrace, and Splunk for monitoring and incident response. Proficient in Linux servers (Debian, Ubuntu, RHEL).
\end{itemize}

\noindent
{\bfseries Entry-Level Monitoring Specialist} \hfill January 2020 - October 2021 \\  
\noindent \href{https://www.opmobility.com/en/plastic-omnium-is-now-opmobility/}{Plastic Omnium Auto Exteriors, s.r.o.} \hfill Lozorno 
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Administered and optimized Centreon and Nagios systems for real-time monitoring. Experienced with Linux and Windows server administration.
\end{itemize}

\noindent
{\bfseries Assistant in the IT department} \hfill June 2018 - September 2018 \\  
\noindent  \href{https://www.ksystem.sk/}{K-system spol. s r. o.} \hfill Žiar nad Hronom   
\begin{itemize} \itemsep -2pt % Reduce space between items
\item Provided technical support for hardware and software issues. Assisted with network administration, including Active Directory management, and configured new IT equipment.
%\item Editing web pages (HTML, CSS) 
%\item Working with cloud (VMware) 
%\item Preparation of new IT equipment
%\item Preparation of documentation for new employees
\end{itemize}


%\noindent
%{\bfseries Lector of Math, English and Informatics} \hfill January 2023 - April 2023 \\  
%\noindent Škola Populo \hfill Remote 
%\begin{itemize} \itemsep -2pt % Reduce space between items
%	\item Lectoring elementary school students during evenings and weekends.
%\end{itemize}

\vspace{0.2in} % Some whitespace between sections


%%%%%%%%%%%%%%%%%%%%%%%%% Certs %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	{\noindent \bfseries Licences and Certifications}
\end{center}

\vspace{0.1pt}


\noindent
{\bfseries \href{https://drive.proton.me/urls/WQCXTSR8C0#8HdkpbN5AP9T}{VIRTUAL HACKING LABS Certificate of Completion \newline and Advanced+ Certificate of Completion}} \hfill earned August 2024 \\ 
\noindent Hands-on penetration testing certifications. \hfill Verification: 245441540 and 244902007
\noindent

\vspace{0.1in}

\noindent
    {\bfseries \href{https://www.credly.com/badges/26299a0a-52db-411c-9df8-f182ff93b8f1/public_url}{Comptia Network+}} \hfill May 2024 - May 2027 \\
    \noindent Vendor-neutral networking certification. \hfill Verification: 2VGEEJS6HFR4QJK6
\noindent

\vspace{0.1in}

\noindent
    {\bfseries \href{https://www.credly.com/badges/2c28f48a-77e5-4b3d-b38e-2b2e355a7eec/public_url}{Comptia Security+}} \hfill January 2024 - January 2027 \\[0.04in]
    \noindent Entry-level IT security certification. \hfill Verification: 5QQ1FCKTKB4QQR9C
\noindent





%\bigskip

%\noindent
%{\bfseries {CyberGame 2023} } \hfill June 2023 \\
%\noindent A game by National Security Authority of Slovak Republic

%\bigskip

%\noindent
%{\bfseries {Digital garage} } \hfill February 2020 \\
%\noindent Free training from Google
\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	{\noindent \bfseries Projects}
\end{center}

\vspace{0.1pt}

\noindent
{\bfseries \href{https://opac.crzp.sk/?fn=detailBiblioFormChildU1JSMF&sid=C0DEB8E07572332BAD240C15805F&seo=CRZP-detail-kniha}{Cyberattack detection using state languages} } \hfill September 2022 - May 2023 \\
\noindent Slovak Technical University \hfill Bratislava 
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Master thesis on detecting cyberattacks using state programming languages, based on MITRE ATT\&CK definitions, with implementation for \href{https://csirt.fei.stuba.sk}{FEI STU's CSIRT}.
\end{itemize}

\noindent
{\bfseries \href{https://github.com/feictf/tp_feictf}{Teaching aid for CTF competitions} } \hfill September 2021 - June 2022 \\
\noindent Slovak Technical University \hfill Bratislava 
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item A team project implementing an infrastructure for organizing CTF competitions based on the \href{https://pwn.college/}{pwn.college} portal, used to teach \href{https://uim.fei.stuba.sk/predmet/i-bispp/}{Information Systems Security} at FEI STU.
\end{itemize}

\noindent
{\bfseries \href{https://opac.crzp.sk/?fn=DETAILBIBLIOFORMChildCB96V&sid=38F43C5054BC4F7F2DBBCFF31F28&seo=CRZP-detail-kniha}{Cyber incident information exchange and sharing} } \hfill September 2020 - June 2021 \\
\noindent Slovak Technical University \hfill Bratislava 
\begin{itemize} \itemsep -2pt % Reduce space between items
	\item Final bachelor thesis on information sharing in cybersecurity, leveraging MISP Open Source Threat Intelligence and CESNET Warden platforms.
\end{itemize}


%\noindent
%{\bfseries \href{https://wiki.wesnoth.org/SlovakTranslation#Preklad}%{Translating Battle for Wesnoth into Slovak language} } \hfill September 2023 - Present \\
%\noindent Personal Hobby Project \hfill Online 
%\begin{itemize} \itemsep -2pt % Reduce space between items
%	\item Translating an open-source videogame, with which I was obsessed as a child into my mother's tongue.
%\end{itemize}

\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%% COMPUTER KNOWLEDGE %%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	{\noindent \bfseries Computer Knowledge}
\end{center}

\vspace{0.1pt}

\noindent
{\bfseries Programming/Scripting}: competent in Python, Bash, \\[0.02in]
familiar with JavaScript, C, Java, Powershell \\[0.04in]
{\bfseries Markup/Style}: \LaTeX, HTML, CSS \\[0.04in]
{\bfseries Databases}: SQL \\[0.04in]
{\bfseries Version Control}: Git \\[0.04in]
{\bfseries Containerization}: Docker  \\[0.04in]
{\bfseries Automation}: Ansible \\[0.04in]
{\bfseries Offensive security}: Metasploit, OpenVAS, BurpSuite \\[0.04in]

\vspace{0.2in} % Some whitespace between sections

%%%%%%%%%%%%%%%%%%%%%%%%%%%% LANGUAGES  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}
	{\noindent \bfseries Languages}
\end{center} 

\vspace{0.1pt}

\noindent
{\bfseries Slovak}: native proficiency \\[0.04in]
{\bfseries English}: professional working proficiency \\[0.04in]
{\bfseries German \& French}: elementary proficiency \\[0.04in]

\vspace{8pt} % Gap between title and text

\begin{center}
	{\noindent \bfseries Selected Links}
\end{center} 

\vspace{0.1pt}

\noindent
{\bfseries Personal website}:
\href{https://fusaty.github.io/}{fusaty.github.io} \\[0.04in]
{\bfseries Github profile}: \href{https://github.com/fusaty}{github.com/fusaty} \\[0.04in]
{\bfseries TryHackMe profile}: \href{https://tryhackme.com/p/michal.fusaty}{tryhackme.com/p/michal.fusaty} \\[0.04in]
{\bfseries LinkedIn profile}: \href{https://linkedin.com/in/michal-fusatý-a41488252}{linkedin.com/in/michal-fusatý-a41488252} \\[0.04in]


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TEACHING EXPERIENCE %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% HONORS & MEMBERSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%% SCHOLARSHIPS & MENTORSHIPS %%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PUBLICATIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% ADDITIONAL INFORMATION %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\begin{center}
%	{\noindent \bfseries Additional information}
%\end{center}

%\noindent
%Drivers licence: \textbf{AM}, \textbf{A1}, \textbf{B1}, \textbf{B} (all active)


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}
